pema application

### 2022-12-05 paper/manuscript.Rmd
fixed typos

Meta-regression models are most commonly estimated using weighted least squares,
with weights determined according to the aforementioned random effects model,
where residual heterogeneity is estimated using restricted maximum likelihood [@pattersonRecoveryInterblockInformation1971; @viechtbauerBiasEfficiencyMetaAnalytic2005].
This approach, henceforth referred to as RMA, has low bias, which means that, across hypothetical replications of a study, the average values of model parameters are close to their true population values [@panityakulEstimatingResidualHeterogeneity2013].
Low bias comes at the cost of higher variance, however,
which means that the estimated values of population parameters vary more from one hypothetical replication to the next.
This phenomenon is known as the *bias-variance trade-off*.
In general, an estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
Regularized approaches to regression intentionally increase bias in order to reduce variance.
This is a sensible approach in the context of small samples, which are common in meta-analyses,
because small samples incur a high risk of overfitting,
and typically have relatively high levels of multicollinearity,
due to the higher probability that extreme values on one moderator coincide with extreme values on another.
In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [see @hastieElementsStatisticalLearning2009].

<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
\begin{align}
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
\end{align}
The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
\begin{align}
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}| (\#eq:prss)
\end{align}
<span id = "whylasso">Note that many other regularizing penalties exist.
This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
and has an analogue in Bayesian estimation,
as explained in the next section.</span>

>>>>

Meta-regression models are most commonly estimated using weighted least squares,
with weights determined according to the aforementioned random effects model,
where residual heterogeneity is estimated using restricted maximum likelihood [@pattersonRecoveryInterblockInformation1971; @viechtbauerBiasEfficiencyMetaAnalytic2005].
This approach, henceforth referred to as RMA, has low bias, which means that, across hypothetical replications of a study, the average values of model parameters are close to their true population values [@panityakulEstimatingResidualHeterogeneity2013].
Low bias comes at the cost of higher variance, however,
which means that the estimated values of population parameters vary more from one hypothetical replication to the next.
This phenomenon is known as the *bias-variance trade-off*.
In general, an estimator with low bias and high variance produces results that generalize worse to new data than an estimator with high bias and low variance.
Regularized approaches to regression intentionally increase bias in order to reduce variance.
This is a sensible approach in the context of small samples, which are common in meta-analyses,
because small samples incur a high risk of overfitting,
and typically have relatively high levels of multicollinearity,
due to the higher probability that extreme values on one moderator coincide with extreme values on another.
In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [see @hastieElementsStatisticalLearning2009].

<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
\begin{align}
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
\end{align}
The resulting parameter estimates perfectly describe linear relations in the present data set, but do not generalize well to new data.
Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
This incentivizes the optimizer to keep the regression coefficients as small as possible.
The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
If $\lambda$ is zero, the shrinkage penalty has no impact.
As $\lambda$ increases,
all coefficients shrink towards zero, ultimately producing the null model.
Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
The LASSO penalized residual sum of squares is given by:
\begin{align}
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}| (\#eq:prss)
\end{align}
<span id = "whylasso">Note that many other regularizing penalties exist.
This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
and has an analogue in Bayesian estimation,
as explained in the next section.</span>
